Title Goes Here

### 2022-02-03 analysis/paper/paper.Rmd
methods update

# Background
- Mau A is an open air site located near the Red River in Yen Bai Province, Northern Vietnam.
- Excavation conducted in 2015 as a part of a UW field school
- A wide array of flakes and stone tools were recovered, n=1058
- Data for the paper comes from caliper measurements of flakes from the 2015 excavation
# Methods
(Note, this is copied largely from the poster, and will require further editing -QH)
-In order to gather the 1058 stone artefacts, excavations were conducted using hand tools and sieved 4 square meter plots of excavated sediment. 
-A custom function was used to transform artefact measurements into outlines
-PCA was conducted on the landmarks outlines
-Reduction categories were based upon dorsal cortex percentage. Flakes with no dorsal cortex were categorized as tertiary flakes, those with up to a dorsal cortex percentage of 50% were considered secondary and those with a dorsal cortex value greater than 50% were considered primary (Bradbury & Carr 1995)
# Results

>>>>

# Background
- Mau A is an open air site located near the Red River in Yen Bai Province, Northern Vietnam.
- Excavation conducted in 2015 as a part of a UW field school
- A wide array of flakes and stone tools were recovered, n=1058
- Data for the paper comes from caliper measurements of flakes from the 2015 excavation
# Methods

The data used for our analysis came from a 2015 dig at Mau A, located in Northern Vietnam, conducted by a University of Washington field school in conjunction with local archaeologists. Raw flake dimension measurements, such as max dimension length and width at various points along the max dimension length, were converted into shape outlines using an R script.

(Note, this is copied largely from the poster, and will require further editing -QH)
-In order to gather the 1058 stone artefacts, excavations were conducted using hand tools and sieved 4 square meter plots of excavated sediment. 
-A custom function was used to transform artefact measurements into outlines
-PCA was conducted on the landmarks outlines
-Reduction categories were based upon dorsal cortex percentage. Flakes with no dorsal cortex were categorized as tertiary flakes, those with up to a dorsal cortex percentage of 50% were considered secondary and those with a dorsal cortex value greater than 50% were considered primary (Bradbury & Carr 1995)
# Results
